### 2014-09-15 Pero_Transcriptome.tex
peerJ submitted

To begin to understand how genes may underlie desert adaptation, we collected 16 individuals from a single population of \textit{P. eremicus} over a two-year time period (2012-2013). These individuals were captured in live traps and then euthanized using isoflurane overdose and decapitation. Immediately post-mortem, the abdominal and pelvic organs were removed, cut in half (in the case of the kidneys), placed in RNAlater and flash frozen in liquid Nitrogen. Removal of the brain, with similar preservation techniques, followed. Time from euthanasia to removal of all organs never exceeded five minutes. Samples were transferred to a -80C freezer at a later date. These procedures were approved by the University of California Berkeley Animal Care and Use Committee and followed guidelines established by the American Society of Mammalogy for the use of wild animals in research \cite{Sikes:2011dz}.

>>>>

To begin to understand how genes may underlie desert adaptation, we collected 16 individuals from a single population of \textit{P. eremicus} over a two-year time period (2012-2013). These individuals were captured in live traps and then euthanized using isoflurane overdose and decapitation. Immediately post-mortem, the abdominal and pelvic organs were removed, cut in half (in the case of the kidneys), placed in RNAlater and flash frozen in liquid Nitrogen. Removal of the brain, with similar preservation techniques, followed. Time from euthanasia to removal of all organs never exceeded five minutes. Samples were transferred to a -80C freezer at a later date. These procedures were approved by the Animal Care and Use Committee located at the University of California Berkeley (protocol number R224) and University of New Hampshire (protocol number 130902) as well as the California Department of Fish and Game (protocol SC-008135) and followed guidelines established by the American Society of Mammalogy for the use of wild animals in research \cite{Sikes:2011dz}.
